\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-31 paper/paper.tex
remove previously introduced error
data cleansing graphics and stuff

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/more_jumps.png}
\caption{Trajectory \textit{} having more than 2,000 jumps}
\label{fig:more_jumps}
\end{figure}

@@

@@

\subsubsection{Calculate distances}
A key functionality of our software is the calculation of the profit per taxi. Therefore, we take three different factors into account:
\begin{enumerate}
    \item Taxi start: As soon as a passenger enters a taxi, he or she has to pay 11 Yuan
    \item Waiting time: There are several reasons why a vehicle has to wait (e.g. for the passenger). We assume, that this time is approxiamtely 10 percent of the ride. An hour of waiting time costs 48 Yuan.
    \item Distance driven: The price of a ride depends on the distance. A typical value is 2.40 Yuan in the city of Shenzhen.
\end{enumerate}
% Die Werte haben sich schon geändert ;)
The prices used for calculation are taken from a website.\footnote{\href{https://www.numbeo.com/taxi-fare/country\_result.jsp?country=China}{https://www.numbeo.com/taxi-fare/country\_result.jsp?country=China}} The values might have changed until now. However, prices will not change in a way, that our calculations become fundamentally wrong.

@@

The simplest way to get the distance of a ride is the usage of spatial points (\textit{ST_POINTS}). This is a data type implemented in SAP Hana, that can be created out of a longitude and a latitude value. Furthermore, there is a function to compute the distance between those points. A single ride starts, when a passenger enters a taxi (occupancy changes from zero to one) and ends, when the passenger leaves (occupancy changes from one to zero). We sum up the lengths between all points sum uo all values for a whole trajectory.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/more_jumps.png}
\caption{Trajectory \textit{32,079} having more than 2,000 jumps}
\label{fig:more_jumps}
\end{figure}

@@

The following graphics depict the amount of records deleted (see figure \ref{fig:records_deleted}) and the amount of completely removed trajectories (see figure \ref{fig:trajectories_deleted}). The quantities are not disjoint amongst the data cleansing steps. In other words, a record or trajectory can occur in multiple sets. Otherwise, the numbers would depend on the order the data cleansing steps were made.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/records_deleted.png}
\caption{Amount of records deleted per data cleansing step}
\label{fig:records_deleted}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{img/trajectories_deleted.png}
\caption{Amount of trajectories deleted per data cleansing step}
\label{fig:trajectories_deleted}
\end{figure}

@@

\subsubsection{Calculate distances}
A key functionality of our software is the calculation of the profit per taxi. Therefore, we take three different factors into account:
\begin{enumerate}
    \item Taxi start: As soon as a passenger enters a taxi, he or she has to pay 11 Yuan.
    \item Waiting time: There are several reasons why a vehicle has to wait (e.g. for the passenger). We assume, that this time is approxiamtely 10 percent of the ride. An hour of waiting time costs 48 Yuan.
    \item Distance driven: The price of a ride depends on the distance. A typical value is 2.40 Yuan in the city of Shenzhen.
\end{enumerate}
% Die Werte haben sich schon geändert ;)
The prices used for calculation are taken from a website.\footnote{\href{https://www.numbeo.com/taxi-fare/country\_result.jsp?country=China}{https://www.numbeo.com/taxi-fare/country\_result.jsp?country=China}} The values might have changed until now. However, prices will not change in a way, that our calculations become fundamentally wrong.

@@

The simplest way to get the distance of a ride is the usage of spatial points (\textit{ST\_POINTS}). This is a data type implemented in SAP Hana, that can be created out of a longitude and a latitude value. Furthermore, there is a function to compute the distance between those points. A single ride starts, when a passenger enters a taxi (occupancy changes from zero to one) and ends, when the passenger leaves (occupancy changes from one to zero). We sum up the lengths between all points sum uo all values for a whole trajectory.
